Combinatorics of the geometry of Wilson loop diagrams

### 2019-03-05 General WLD combinatorics.tex
mostly grammatical changes to 3.7

Note that if $p = (i, j)$, then we can consider two obvious restrictions of $W$, namely \bas W|_{\cP_{in} \cup p} \quad \textrm{and} \quad  W|_{\cP_{out}\cup p}, \eas where the set of non-supportive vertices of  $W|_{\cP_{in} \cup p}$ is $V_{out}$ and  the set of non-supportive vertices of  $W|_{\cP_{out} \cup p}$ is $V_{in}$. That is, these restrictions contain the propagators on the inside and outside of $(p, <_i)$ respectively, as well as $p$ itself. \footnote{If we denote $V \subset [n]$ and $Q = \Prop(V^c)$, then we can write \bas M(W|_{Q^c}) = M(W)/F(Q) \oplus M_{\emptyset, n-|i-j+1|} \eas where  $M_{\emptyset, k}$ is the matroid of rank $0$ on a set of $k$. That is $M_{\emptyset, n-|i-j+1|} =M((\emptyset, n-|i-j+1|))$. }

@@

Start by choosing a propagator $p_1 = (j_1,j_1+2)$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}).  If it is part of one of the configurations we are looking for then we are done, 
%a configuration \eqref{eq:2 prop config} we are done,
so suppose otherwise. 
By assumption: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex is supported.  Therefore there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.  Orient $q_1 = (i_1, k_1)$ such that  $p_1 \in \cP_{out}(q_1)$, (that is $(q_1, <_{i_1})$).

@@

Call let $W_r := W|_{\cP_{in} \cup q_r}$. By the original hypotheses on $W$ every vertex in $V_{in}(q_r)$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $V(q_r)$ because these vertices support $q_r$. By construction, the remaining vertices of $W|_{\cP_{in} \cup p}$, i.e. $V_{out}(q_r)$ are non-supporting.

@@

Write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$.
There are two cases to consider.
The first case is that $i_r \leq j_{r+1} \leq i_r+2$ and $k_r-2 \leq j_{r+1}+2 \leq k_{r}$ (so $p_{r+1}$ has one end before $i_{r} + 3$ and the
other after $k_{r} - 2$).  Then since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length $\leq 6$.  By the minimality assumption on $q_r$ no propagator in $W_r$ has $q_r$ on one sid eand $p_{r+1}$ on the other side, so there is any propagator in $W_r$ other than $p_{r+1}$ itself must be of the form $(i,j)$ with $i_r\leq i, j\leq i_r+2$ or $k_r-1 \leq i,j\leq k_r$ and hence be of length 2, and so we have configuration \ref{item pair of 2s} which we have already assumed does not occur.  Consequently, $\cP_{in}(q_r)$ contains only $p_{r+1}$ and so we have \ref{item big and 2} which again we have assumed does not occur.
Therefore the first case cannot occur.

The second case is that one of the following three things happen
\begin{itemize}
\item $i_r+3 \leq j_{r+1}\leq k_r-3$ or $i_r+3 \leq j_{r+1}+2\leq k_r-3$,
\item $i_r = j_{r+1}$, or 
\item $k_r-2 = j_{r+1}$
\end{itemize}
(Phrased more causually, this is that $p_{r+1}$ has either at least one end on an edge in the interval $[i_r+3, k_r-2]$ or both ends lie in $[i_r, i_r+3]$ or both ends lie in $[k_r-2, k_r+1]$.)
These situations all behave similarly.
By symmetry it suffices to only consider the second situation and the second possiblity of the first situation. Note that since $j_{r+1}+4 \leq k_r-1$ in both situations, and $j_{r+1}+4 \in V_{in}(q_r)$, thus $j_{r+1}+4$ is supported by a propagator in $W_r$ other than $q_r$.  Let $t$ be this propagator.  Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, we must have that the length of $t$ is $\geq 4$.  If $q_r$ and $p_{r+1}$ were on different sides of $t$ then this would contradict the minimal length hypothesis on $q_r$.  Therefore $t$ has all the previous $q_i$ and $p_i$ on the same side and length $\geq 4$ and so we may set $q_{r+1} = t$ to continue the induction.

>>>>

Given a propagator $p = (i, j)$ oriented $(p, <_i)$,  we can consider two obvious restrictions of $W$, namely \bas W|_{\cP_{in} \cup p} \quad \textrm{and} \quad  W|_{\cP_{out}\cup p}, \eas where the set of non-supportive vertices of  $W|_{\cP_{in} \cup p}$ is $V_{out}$ and  the set of non-supportive vertices of  $W|_{\cP_{out} \cup p}$ is $V_{in}$. That is, these restrictions contain the propagators on the inside and outside of $(p, <_i)$ respectively, as well as $p$ itself. \footnote{If we denote $V \subset [n]$ and $Q = \Prop(V^c)$, then we can write \bas M(W|_{Q^c}) = M(W)/F(Q) \oplus M_{\emptyset, n-|i-j+1|} \eas where  $M_{\emptyset, k}$ is the matroid of rank $0$ on a set of $k$. That is $M_{\emptyset, n-|i-j+1|} =M((\emptyset, n-|i-j+1|))$. }

@@

Start by choosing a propagator $p_1 = (j_1,j_1+2)$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}).  If it is part of one of the configurations we are looking for then we are done, 
%a configuration \eqref{eq:2 prop config} we are done,
so suppose otherwise. 
By assumption: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex supports at least one propagator.  Therefore there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.  Orient $q_1 = (i_1, k_1)$ such that  $p_1 \in \cP_{out}(q_1)$, (that is $(q_1, <_{i_1})$).

@@

Call let $W_r := W|_{\cP_{in} \cup q_r}$. By the original hypotheses on $W$ every vertex in $v \in V_{in}(q_r)$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support at least one propagator ($|\Prop(v)| \geq 1$), while the same is true for $V(q_r)$ because these vertices support $q_r$. By construction, the remaining vertices of $W|_{\cP_{in} \cup {q_r}}$, i.e. $V_{out}(q_r)$, are non-supporting.

@@

Write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$.
There are two cases to consider.
The first case is that $i_r \leq j_{r+1} \leq i_r+2$ and $k_r-2 \leq j_{r+1}+2 \leq k_{r}$ (so $p_{r+1}$ has one end before $i_{r} + 3$ and the
other after $k_{r} - 2$).  Then since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length $\leq 6$.  By the minimality assumption on $q_r$ no propagator in $W_r$ has $q_r$ on one side and $p_{r+1}$ on the other side. Therefore, any propagator in $W_r$ other than $p_{r+1}$ itself must be of the form $(i,j)$ with $i_r\leq i, j\leq i_r+2$ or $k_r-2 \leq i,j\leq k_r$. That is, this propagator must be of length 2, and so we have configuration \ref{item pair of 2s} which we have already assumed does not occur.  Consequently, $\cP_{in}(q_r)$ contains only $p_{r+1}$ and so we have congifuratin  \ref{item big and 2} from the lemma statement which again we have assumed does not occur.
Therefore this first case cannot occur.

The second case is that one of the following three things happen (we continue to write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$) 
\begin{itemize}
\item $i_r+3 \leq j_{r+1}\leq k_r-3$ or $i_r+3 \leq j_{r+1}+2\leq k_r-3$,
\item $i_r = j_{r+1}$, or 
\item $k_r-2 = j_{r+1}$
\end{itemize}
(Phrased more causually, this is that $p_{r+1}$ has either at least one end on an edge bounded by the vertices in the interval $[i_r+3, k_r-2]$ or both ends lie in $[i_r, i_r+3]$ or both ends lie in $[k_r-2, k_r+1]$.)
These situations all behave similarly.
By symmetry it suffices to only consider the second situation and the second possiblity of the first situation. Note that since $j_{r+1}+4 \leq k_r-1$ in both situations, and $j_{r+1}+4 \in V_{in}(q_r)$, thus $j_{r+1}+4$ is supported by a propagator in $W_r$ other than $q_r$.  Let $t$ be this propagator.  Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, we must have that the length of $t$ is $\geq 4$.  If $q_r$ and $p_{r+1}$ were on different sides of $t$ then this would contradict the minimal length hypothesis on $q_r$.  Therefore $t$ has all the previous $q_i$ and $p_i$ on the same side and length $\geq 4$ and so we may set $q_{r+1} = t$ to continue the induction.
